---
title: "HW4"
author: "Haoran Zhang"
date: "2021/11/18"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(parallel)
```


## Problem 1: Make sure your code is nice
Rewrite the following R functions to make them faster. It is OK (and recommended) to take a look at Stackoverflow and Google
```{r}
temp <- function(n = 100, k = 4, lambda = 4) {
  x <- NULL
  for (i in 1:n)
    x <- rbind(x, rpois(k, lambda))
  return(x)
}
mat<-temp(5,10)
```


```{r}
# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}
fun1(mat)
```



```{r}
fun1alt <- function(mat) {
  idx<-rowSums(mat)
  idx
}
fun1alt(mat)
```

```{r}
# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}
fun2(mat)
```

```{r}
fun2alt <- function(mat) {
  ans<-t(apply(mat, 1, cumsum))
  ans
}
fun2alt(mat)
```

```{r}
# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)

# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), unit = "relative", check = "equivalent"
)

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), unit = "relative", check = "equivalent"
)
```
## Problem 2: Make things run faster with parallel computing
The following function allows simulating PI
```{r}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}
# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132
```
In order to get accurate estimates, we can run this function multiple times, with the following code:
```{r}
# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})
```
Rewrite the previous code using parLapply() to make it run faster. Make sure you set the seed using clusterSetRNGStream():
```{r}
cl <- makePSOCKcluster(4)
clusterSetRNGStream(cl, 123)
clusterExport(cl,varlist = c("sim_pi"), envir = environment())

system.time({
  ans <- unlist(parLapply(cl, 1:4000, sim_pi, n = 10000))
  print(mean(ans))
  stopCluster(cl)
})
```


```{r}
# YOUR CODE HERE
system.time({
  # YOUR CODE HERE
  ans <- # YOUR CODE HERE
  print(mean(ans))
  # YOUR CODE HERE
})
```

## SQL
Setup a temporary database by running the following chunk
```{r}
# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)
```

## Question 1
How many many movies is there avaliable in each rating catagory.
```{sql, connection=con}
select rating, count(film_id) as count 
from film 
group by rating
```

## Question 2
What is the average replacement cost and rental rate for each rating category.
```{sql, connection=con}
select rating, avg(replacement_cost), avg(rental_rate)
from film
group by rating
```

## Question 3
Use table film_category together with film to find the how many films there are witth each category ID
```{sql, connection=con}
select category_id, count(film_category.film_id) as count_film_id
from film inner join film_category on film.film_id=film_category.film_id
group by category_id
```
Create a table 
```{r}
Q3<-dbGetQuery(con, "select category_id, count(film_category.film_id) as count_film_id
from film inner join film_category on film.film_id=film_category.film_id
group by category_id")
dbWriteTable(con, "Q3", Q3)
```

## Question 4
Incorporate table category into the answer to the previous question to find the name of the most popular category.
```{sql, connection=con}
select Q3.category_id, category.name, max(count_film_id) as count
from Q3 inner join category on Q3.category_id=category.category_id
```
clean up
```{r}
dbDisconnect(con)
```

